---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# HeadR [![Build Status](https://travis-ci.org/jumpingrivers/headR.svg?branch=master)](https://travis-ci.org/jumpingrivers/headR)

HeadR is a package for creating social media summary cards to share your articles. HeadR currently supports two types of meta tags: twitter and open graph. Usually you would have to write meta tags within your html file for them to have a visually appealing sharing format. An example of how you would add these meta tags to your Rmd document is as shown:

```
---   
output: 
  html_document: 
    includes:
      in_header: twitter_card.html
---
```

The file `twitter_card.html` contains meta tag information is the output of running the function `headR::add_twitter_card()`. More specifically:

```{r, eval = FALSE}
headR::add_twitter_card(title = "This is the title!", file = "twitter_card.html")
```

Note, the html file containing the meta tags must be created before you knit the document. 


