---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# HeadR [![Build Status](https://travis-ci.org/jumpingrivers/headR.svg?branch=master)](https://travis-ci.org/jumpingrivers/headR)

HeadR is a package for creating social media summary cards to share your articles. Usually you would have to write meta tags within your HTML file to do this. An example of how you would add these meta tags to your Rmd document is as shown:

```{r, eval = FALSE}
---
output: 
  html_document: 
    includes:
      in_header: twitter_card.html
---  

## Testing

headR::add_twitter_card(title = "This is the title!", file = "twitter_card.html")
```

Full examples are contained withing the `inst` directory within the package: 

## `add_twitter_card()` for twitter example

Within `inst -> examples`, there is an Rmd document called `twitter_large_summary_image.Rmd`.  When knitted, this document creates a html page that we have stored on `www.jumpingrivers.com`. This contains the code that was run to put the meta tags in the header. Copy and paste this page URL into the [twitter card validator](https://cards-dev.twitter.com/validator) and you will see what the example twitter card looks like. 

## `add_og_card()` for open graph example

Again, within `inst -> examples`, there is an Rmd document, this time called `open_graph.Rmd`. When knitted, this document creates a html page that we have stored on `www.jumpingrivers.com`. The Rmd document also contains the code that was run to put the meta tags in the header. I have found the best way to preview open graph sharing cards is to download the chrome extension [Open Graph Preview](https://chrome.google.com/webstore/detail/open-graph-preview/ehaigphokkgebnmdiicabhjhddkaekgh/related).

