---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# HeadR [![Build Status](https://travis-ci.org/jumpingrivers/headR.svg?branch=master)](https://travis-ci.org/jumpingrivers/headR)

HeadR is a package for creating social media summary cards to share your articles. HeadR currently supports two types of meta tags: twitter and open graph. Usually you would have to write meta tags within your html file for them to have a visually appealing sharing format. An example of how you would add these meta tags to your Rmd document is as shown:

```
---   
output: 
  html_document: 
    includes:
      in_header: twitter_card.html
---
```

The file `twitter_card.html` contains meta tag information is the output of running the function `headR::add_twitter_card()`. More specifically:

```{r, eval = FALSE}
headR::add_twitter_card(title = "This is the title!", file = "twitter_card.html")
```

Note, the html file containing the meta tags must be created before you knit the document. 

Full examples are contained withing the `inst` directory within the package: 

## Example: `add_twitter_card()` for Rmd knitted documents

Within `inst -> examples`, there is an Rmd document called `twitter_large.Rmd`.  When knitted, this document creates a html page containing twitter meta tags that we have stored on `www.jumpingrivers.com`. The code code that was run to create the meta tags is also in the document. Copy and paste this page URL into the [twitter card validator](https://cards-dev.twitter.com/validator) and you will see what the example twitter card looks like. 

## Example: `add_og_card()` for Rmd knitted documents

Again, within `inst -> examples`, there is an Rmd document, this time called `open_graph.Rmd`. When knitted, this document creates a html page containing open graph meta tags that we have stored on `www.jumpingrivers.com`. The Rmd document also contains the code that created the meta tags in the header. I have found the best way to preview open graph sharing cards is to download the chrome extension [Open Graph Preview](https://chrome.google.com/webstore/detail/open-graph-preview/ehaigphokkgebnmdiicabhjhddkaekgh/related).

## Example: `add_twitter_card()` for Rmd knitted slides

Within `inst -> examples`, there is an Rmd document, this time called `twitter_slides.Rmd`. When knitted, this produces html slides. Again, using the same technique, we can add meta tags into the header of the document. This time we've added the same meta tags as the first `add_twitter_card()` example (about bees). We have also stored these slides on `www.jumpingrivers.com`. To preview the twitter card copy and paste the URL into the [twitter card validator.](https://cards-dev.twitter.com/validator)
